Data analysis for employee cluster assessment

### 2023-07-11 04. Analysis/scripts/03-02-data-analysis-employee-cluster-assessing-clusters.Rmd
Update 03-02-data-analysis-employee-cluster-assessing-clusters.Rmd
Developing code for PCA data visualization

---
title: "Data analysis for employee cluster assessment"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: united
    highlight: tango
    code_folding: hide
params:
  author: "Ben Jaques-Leslie"
  project_number: 2312
  project_name: "Occupancy Patterns"
  google_drive_home: "G:/Shared drives/MSG Projects/1.0 Real Estate Solutions (LQ1)/2312 Work Patterns"
  data_folder_1: "prepared-data"
  data_file_1: "clusters-employee-2023-06-08.rdata"
  data_file_2: "prep_employees_2023-05-24.rdata"
  in_number_of_clusters: 5
  in_specification: "scale_working_proportion_pairs_1_10"

@@

@@

>>>>

---
title: "Data analysis for employee cluster assessment"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: united
    highlight: tango
    code_folding: hide
params:
  author: "Ben Jaques-Leslie"
  project_number: 2312
  project_name: "Occupancy Patterns"
  google_drive_home: "G:/Shared drives/MSG Projects/1.0 Real Estate Solutions (LQ1)/2312 Work Patterns"
  data_folder_1: "prepared-data"
  data_file_1: "clusters-employee-2023-06-08.rdata"
  data_file_2: "prep_employees_2023-05-24.rdata"
  in_number_of_clusters: 5
  in_number_of_clusters_start: 1
  in_number_of_clusters_end: 10
  in_specification: "scale_working_proportion_pairs_1_10"
  in_seed: 27

@@

```{r}
set.seed(params$in_seed)
```

@@

```{r}
source(here::here("04. Analysis","scripts","select_cluster_cols.R"))
```

```{r}
source(here::here("04. Analysis","scripts","make_clusters.R"))
```

#### Making clusters visualizations using PCA

```{r}
source(here::here("04. Analysis","scripts","make_fviz_clusters.R"))
```

#### Creating d for cluster analysis

```{r}
source(here::here("04. Analysis","scripts","prep_employees_to_d.R"))
```

#### Making clusters  visualizations using PCA of different sizes, but only for `d` and adding specification

```{r}
make_fviz_clusters_d <- function(in_specification,
                            in_scale_or_rank,
                            in_working_or_observation_window,
                            in_weekday_correlation,
                            in_number_of_clusters_start,
                            in_number_of_clusters_end)
{
  make_fviz_clusters(
    in_data = d,
    in_scale_or_rank = in_scale_or_rank,
    in_working_or_observation_window = in_working_or_observation_window,
    in_weekday_correlation = in_weekday_correlation,
    in_number_of_clusters_start = in_number_of_clusters_start,
    in_number_of_clusters_end = in_number_of_clusters_end
  ) %>%
    mutate(specification = in_specification)
}
```

```{r}
source(here::here("04. Analysis","scripts","make_specs.R"))
```

```{r}
v <- 
  specs %>%
  pmap_dfr(make_fviz_clusters_d)
```

```{r}
v %>% #count(specification)
  filter(specification == params$in_specification) %>% 
  .$fviz_cluster
```
